An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-24 tex/main.tex
Change title: numerical -> empirical
Add a `main.csv` data that makes all analysis easier.

% Title
\title{A numerical study of fixation probabilities for strategies in the
       Iterated Prisoner's Dilemma}
\author{Marc Harper \and Vincent Knight} % TODO Authors?
\date{}

@@

Further deviations from the analytical model occur when interactions between
players are subject to uncertainty. This is referred to as noise and has been
considered in the IPD setting in \cite{Bendor1993, Nowak1993, Wu1995}. Noise is
also considered here.

@@

Figures~\ref{fig:fixation_heatmap_1_std},~\ref{fig:fixation_heatmap_n_over_2_std}
and~\ref{fig:fixation_heatmap_n_over_2_noise} shows the fixation rates of each
player on the y axis against each player on the x axis.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_1_std.pdf}
        \caption{\((N,i)=(4, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_1_std.pdf}
        \caption{\((N,i)=(6, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_1_std.pdf}
        \caption{\((N,i)=(8, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_1_std.pdf}
        \caption{\((N,i)=(10, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_1_std.pdf}
        \caption{\((N,i)=(12, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_1_std.pdf}
        \caption{\((N,i)=(14, 1)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
    \label{fig:fixation_heatmap_1_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_std.pdf}
        \caption{\((N,i)=(4, 2)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_std.pdf}
        \caption{\((N,i)=(6, 3)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_std.pdf}
        \caption{\((N,i)=(8, 4)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_std.pdf}
        \caption{\((N,i)=(10, 5)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_std.pdf}
        \caption{\((N,i)=(12, 6)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_std.pdf}
        \caption{\((N,i)=(14, 7)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{N/2}\) of all strategies}
    \label{fig:fixation_heatmap_n_over_2_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_noise.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_noise.pdf}
        \caption{\((N,i)=(4, 2)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_noise.pdf}
        \caption{\((N,i)=(6, 3)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_noise.pdf}
        \caption{\((N,i)=(8, 4)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_noise.pdf}
        \caption{\((N,i)=(10, 5)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_noise.pdf}
        \caption{\((N,i)=(12, 6)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_noise.pdf}
        \caption{\((N,i)=(14, 7)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probabilities of all strategies with noise}
    \label{fig:fixation_heatmap_n_over_2_noise}
\end{figure}

Figure~\ref{fig:invasion_boxplot_std} shows the fixation probabilities for each
strategy when invading another strategy.
Figure~\ref{fig:resistance_boxplot_std} shows the fixation probabilities for
each strategy when resisting another strategy.
Figure~\ref{fig:coexistance_boxplot_std} shows the fixation probabilities for
each strategy when initially coexisting with another strategy.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/invasion_boxplot_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/invasion_boxplot_4_std.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/invasion_boxplot_6_std.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_8_std.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_10_std.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_12_std.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_14_std.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Invasion fixation probabilities of all strategies}
    \label{fig:invasion_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/resistance_boxplot_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/resistance_boxplot_4_std.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/resistance_boxplot_6_std.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_8_std.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_10_std.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_12_std.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_14_std.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Resistance fixation probabilities of all strategies}
    \label{fig:resistance_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_4_std.pdf}
        %\caption{\(N=4\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_6_std.pdf}
        %\caption{\(N=6\)}
    %\end{subfigure}%

    \begin{subfigure}[htbp]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_8_std.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_10_std.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_12_std.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_14_std.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Coexistance fixation probabilities of all strategies}
    \label{fig:coexistance_boxplot_std}
\end{figure}

Figures~\ref{fig:ranks_v_size_invasion},~\ref{fig:ranks_v_size_resistance}
and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
population size in the standard and noisy settings. Note that these ranks are
not necessarily integers as group ties are given the average rank.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invasion.pdf}
    \caption{Invasion}
    \label{fig:ranks_v_size_invasion}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resistance.pdf}
    \caption{Resistance}
    \label{fig:ranks_v_size_resistance}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invasion.pdf}
    \caption{Relationship between Median rank for population size for strategies
    invading}
    \label{fig:relationship_ranks_v_size_invasion}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resistance.pdf}
    \caption{Relationship between Median rank for population size for strategies
    resisting}
    \label{fig:relationship_ranks_v_size_resistance}
\end{figure}

@@

Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
show the coefficients and \(R^2\) value of the linear model relating the rank in
a particular sized population to the ranks in other populations sizes.
% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
% does show that the coefficient of the N=2 column is always low whereas the
% coefficient of the N=14 column is high even in the N=4 row. So how well you do
% in  a match (N=2) has got very little to do with an evolutionary process.

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_invasion.tex"}
        \caption{Linear model coefficients for ranks for invasion}
        \label{tbl:linear_coeficients_invasion}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_resistance.tex"}
        \caption{Linear model coefficients for ranks for resistance}
        \label{tbl:linear_coeficients_resistance}
    \end{subfigure}

@@

% TODO Discuss effect of size on performance of strategies. Relate to Press and
% Dyson work: "ZD strategies win matches but not tournaments".
% TODO Include discussion about noise.

>>>>

% Title
\title{An empirical study of fixation for strategies in the
       Iterated Prisoner's Dilemma}
\author{Marc Harper \and Vincent Knight} % TODO Authors?
\date{}

@@

Further deviations from the analytical model occur when interactions between
players are subject to uncertainty. This is referred to as noise and has been
considered in the IPD setting in \cite{Bendor1993, Nowak1993, Wu1995}.

@@

Figures~\ref{fig:fixation_heatmap_invade}
and~\ref{fig:fixation_heatmap_coexist} show the fixation rates of each
player on the y axis against each player on the x axis.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_invade.pdf}
        \caption{\((N,i)=(4, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_invade.pdf}
        \caption{\((N,i)=(6, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_invade.pdf}
        \caption{\((N,i)=(8, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_invade.pdf}
        \caption{\((N,i)=(10, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
        \caption{\((N,i)=(12, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_invade.pdf}
        \caption{\((N,i)=(14, 1)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
    \label{fig:fixation_heatmap_invade}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_coexist.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_coexist.pdf}
        \caption{\((N,i)=(4, 2)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_coexist.pdf}
        \caption{\((N,i)=(6, 3)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_coexist.pdf}
        \caption{\((N,i)=(8, 4)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_coexist.pdf}
        \caption{\((N,i)=(10, 5)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_coexist.pdf}
        \caption{\((N,i)=(12, 6)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_coexist.pdf}
        \caption{\((N,i)=(14, 7)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{N/2}\) of all strategies}
    \label{fig:fixation_heatmap_coexist}
\end{figure}

Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
strategy when invading another strategy.
Figure~\ref{fig:resistance_boxplot_resist} shows the fixation probabilities for
each strategy when resisting another strategy.
Figure~\ref{fig:coexistance_boxplot_coexist} shows the fixation probabilities for
each strategy when initially coexisting with another strategy.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_4_invade.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_6_invade.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_8_invade.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_10_invade.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_14_invade.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Invasion fixation probabilities of all strategies}
    \label{fig:invasion_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_resist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_4_resist.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_6_resist.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_8_resist.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_10_resist.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_14_resist.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Resistance fixation probabilities of all strategies}
    \label{fig:resistance_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_coexist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_4_coexist.pdf}
        %\caption{\(N=4\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_6_coexist.pdf}
        %\caption{\(N=6\)}
    %\end{subfigure}%

    \begin{subfigure}[htbp]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_8_coexist.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_10_coexist.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_12_coexist.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_14_coexist.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Coexistance fixation probabilities of all strategies}
    \label{fig:coexistance_boxplot_std}
\end{figure}

Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
population size in the standard and noisy settings. Note that these ranks are
not necessarily integers as group ties are given the average rank.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invade.pdf}
    \caption{invade}
    \label{fig:ranks_v_size_invade}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resist.pdf}
    \caption{resist}
    \label{fig:ranks_v_size_resist}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invade.pdf}
    \caption{Relationship between Median rank for population size for strategies
    invading}
    \label{fig:relationship_ranks_v_size_invasion}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resist.pdf}
    \caption{Relationship between Median rank for population size for strategies
    resisting}
    \label{fig:relationship_ranks_v_size_resistance}
\end{figure}

@@

Tables~\ref{tbl:linear_coeficients_invade},~\ref{tbl:linear_coeficients_resist}
and~\ref{tbl:linear_coeficients_coexist} show the coefficients and \(R^2\) value
of the linear model relating the rank in a particular sized population to the
ranks in other populations sizes.
% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
% does show that the coefficient of the N=2 column is always low whereas the
% coefficient of the N=14 column is high even in the N=4 row. So how well you do
% in  a match (N=2) has got very little to do with an evolutionary process.

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_invade.tex"}
        \caption{Linear model coefficients for ranks for invasion}
        \label{tbl:linear_coeficients_invade}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_resist.tex"}
        \caption{Linear model coefficients for ranks for resistance}
        \label{tbl:linear_coeficients_resist}
    \end{subfigure}

@@

% TODO Discuss effect of size on performance of strategies. Relate to Press and
% Dyson work: "ZD strategies win matches but not tournaments".
